State of the Practice of Lattice Boltzmann Method Software Development

### 2021-06-16 StateOfPractice/Peter-Notes/Report/Report.tex
moved research questions to Introduction

\subsection{Purpose}

The LBM software packages are assessed in order to answer the research questions found in the Appendix in \ref{researchquestions}. They are assessed for a given set of quality attributes using quantitative and qualitative data. The qualities are defined in Section \ref{softwarequalities}. Qualitative data is gathered from interviews with software package developers. The interview questions are listed in the Appendix in \ref{interviewquestions}. Quantitative data is measured using the quality metrics listed in the Appendix in \ref{measurementtemplate2}. In this context the purposes of the report are as follows:

@@

In the course of this assessment we updated the methodology that was used during previous assessments. Details of the new methodology are in \citep{methodology2020}. The previous set of research questions were critically assessed and modified. The updated questions are listed in the Appendix in \ref{researchquestions}. In this re-boot we collected more quantitative and qualitative data, focused on software quality attributes, and added more measures, including collecting empirical data and interviewing developers. We have also added a domain analysis to better characterize the functionality provided by the software, and have leveraged the expertise of a domain expert. As in past assessments, the collected data was combined to rank the software using the Analytic Hierarchy Process (AHP). The domain expert was consulted to verify the ordering.

@@

In this project we set out to answer the research questions found in the Appendix in \ref{researchquestions} for the LBM SCS domain. The process involved systematically measuring and analyzing members of this software family along the quality attributes found in Section \ref{softwarequalities}. This included gathering quantitative and qualitative measurements. A goal of the project was to produce a quality assessment for LBM software packages.

@@

The quality measurements in this assessment rely on the gathering and analyzing of raw and processed empirical data related to the research questions listed in the Appendix in \ref{researchquestions}.

@@

\subsection{Research Questions}\label{researchquestions}
	The following are the research questions that are considered.

>>>>

\subsection{Purpose}\label{purpose}

The LBM software packages are assessed in order to answer the following research questions:

The packages are assessed for a given set of quality attributes using quantitative and qualitative data. The qualities are defined in Section \ref{softwarequalities}. Qualitative data is gathered from interviews with software package developers. The interview questions are listed in the Appendix in \ref{interviewquestions}. Quantitative data is measured using the quality metrics listed in the Appendix in \ref{measurementtemplate2}. In this context the purposes of the report are as follows:

@@

In the course of this assessment we updated the methodology that was used during previous assessments. Details of the new methodology are in \citep{methodology2020}. The previous set of research questions were critically assessed and modified. The updated questions are listed in Section \ref{purpose}. In this re-boot we collected more quantitative and qualitative data, focused on software quality attributes, and added more measures, including collecting empirical data and interviewing developers. We have also added a domain analysis to better characterize the functionality provided by the software, and have leveraged the expertise of a domain expert. As in past assessments, the collected data was combined to rank the software using the Analytic Hierarchy Process (AHP). The domain expert was consulted to verify the ordering.

@@

In this project we set out to answer the research questions listed in Section \ref{purpose} for the LBM SCS domain. The process involved systematically measuring and analyzing members of this software family along the quality attributes found in Section \ref{softwarequalities}. This included gathering quantitative and qualitative measurements. A goal of the project was to produce a quality assessment for LBM software packages.

@@

The quality measurements in this assessment rely on the gathering and analyzing of raw and processed empirical data related to the research questions listed in Section \ref{purpose}.

@@
